---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


<!-- badges: start -->
<!-- badges: end -->

# align

Methods for the alignment and merging of partially or inexactly
aligned data.

## Installation

You can install the development version of align from [GitHub](https://github.com/). 

(As well as `R`, the package also includes some `c++` code. So, if you have not used similar before you may need to install a compiler, for example [Rtools](https://cran.r-project.org/bin/windows/Rtools/) if you are using Windows).


```{r install, eval=FALSE}
install.packages("devtools") #if you don't already have it
devtools::install_github("KarlRopkins/align")
```



## Contributing
Contributions are very welcome, using tidyverse contribution and code of conduct but not as strict as them regarding coding style...   

## License
GPL-3
